Tables

### 2019-06-24 code/tables.rmd
Added original tau estimates to table 3 + changed RBIS to manual for SMD

#fit a random effects model to all empirical data
#Each set of input datapoints is meta-analyzed as per the original replication project
#Function 'est_heterogen_smd_raw' is sourced
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date

@@

#NB! note that for low vs. high category scales, the I2 lower bound is zero, but after transformation
#the tau2 lower bound is *not* zero. This is an indication of the problems with effect size tranformations.

res <- res %>%
  mutate(tau = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
         tau_ci.lb = sqrt(res2$tau2.lb),
         tau_ci.ub = sqrt(res2$tau2.ub),
         r = res2$r)

#Add rp and k to the data-frame and prep for table
het <- dat %>% 
  select(rp, Site, effect, effect_type) %>% 
  group_by(rp, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  ungroup()

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_power) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 1), nsmall = 1)), ", ", trimws(format(round(s_ci.ub, 1), nsmall = 1)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         s_I2 = format(round(s_I2, 1), nsmall = 1),
         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
         tau = format(round(tau, 3), nsmall = 3)) %>% #rounded here instead of in table function because should have 4 digits
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau, tau_ci, zero, small, medium, large)

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau$", "$\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 10, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 10, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, K = no. primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations. $I^2$ and its confidence intervals are for original effect size specifications whereas $/tau^2$ and its confidence intervals are for transformed r* effect sizes. Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences") %>% 
  landscape()

>>>>

#fit a random effects model to all empirical data
#Each set of input datapoints is meta-analyzed as per the original replication project
#Function 'est_heterogen_smd_raw' is sourced
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
  mutate(tau = sqrt(tau2),
         tau_ci.lb = sqrt(tau2_ci.lb),
         tau_ci.ub = sqrt(tau2_ci.ub)) %>% 
  select(-tau2, - tau2_ci.lb, -tau2_ci.ub) #drop redundant variables

@@

res <- res %>%
  mutate(r = res2$r,
         tau_r = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
         tau_r_ci.lb = sqrt(res2$tau2.lb),
         tau_r_ci.ub = sqrt(res2$tau2.ub))

#Add rp and k to the data-frame and prep for table
het <- dat %>% 
  select(rp, Site, effect, effect_type) %>% 
  group_by(rp, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  ungroup()

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_power) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 1), nsmall = 1)), ", ", trimws(format(round(s_ci.ub, 1), nsmall = 1)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         s_I2 = format(round(s_I2, 1), nsmall = 1),
         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
         tau = format(round(tau, 3), nsmall = 3),
         tau_r = format(round(tau_r, 3), nsmall = 3),
         tau_r_ci = paste0("[", trimws(format(round(tau_r_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_r_ci.ub, 3), nsmall = 3)), "]")) %>% #rounded here instead of in table function because should have 4 digits
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau, tau_ci, r, tau_r, tau_r_ci, zero, small, medium, large)

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "r*" , "r* $\\tau$", "r* $\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 12, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 12, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, K = no. primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations. $I^2$ and its confidence intervals are for original effect size specifications whereas $\tau$ and its confidence intervals are for transformed r* effect sizes. Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/",
           alphabet = "These effects were simulated as standardized mean differences") %>% 
  landscape()
